Developing data load and processing

### 2020-10-16 dev/raw_data_preprocessing.Rmd
Preprocessing final data

@@

```{r}
typeof(patients_to_merge$patient_id1)
complete_data_merged <- merge_patients(complete_data, patients_to_merge)

complete_data$patient_data %>% filter(hospital_id == "Oriik", patient_id == 3)
complete_data_merged$breathing_data %>% filter(hospital_id == "cTdij")
complete_data_merged$patient_data %>% filter(hospital_id == "cTdij")
complete_data$patient_data %>% filter(hospital_id == "cTdij")

@@

```{r}
complete_data <- merge_hospitals(complete_data, hospitals_to_merge)

complete_data$patient_data %>% filter(hospital_id == "Oriik")
```

@@

>>>>

## Some more checks

unknown_breathing

```{r}
max_days <- complete_data$breathing_data %>% group_by(hospital_id, patient_id) %>%
  summarise(max_day = max(day))

max_max_day = max(max_days$max_day)

crossing(max_days, day = 0:max_max_day) %>% filter(day <= max_day, day >= 0) %>%
  anti_join(complete_data$breathing_data, by = c("hospital_id", "patient_id", "day"))

complete_data$breathing_data %>% filter(is.na(breathing)) 
```

Markers outside breathing

@@

```{r}
typeof(patients_to_merge$patient_id1)
complete_data_merged_1 <- merge_patients(complete_data, patients_to_merge)
```

```{r}
complete_data_merged <- merge_hospitals(complete_data_merged_1, hospitals_to_merge)

complete_data_merged$patient_data %>% filter(hospital_id == "Oriik")

@@

```{r}
complete_data <- complete_data_merged
```

```{r}
```

@@

Patient counts

```{r}
complete_data$patient_data %>% group_by(hospital_id) %>%
  summarise(n())
```
